Boundary condition changing operators and singular vectors of Virasoro and affine Lie algebra modules

### 2013-02-09 AffineLieAlgebras/Simons/talk.tex
Some work on the talk

Hello!
It's a great pleasure for me to be here in Simons Center for geometry and physics. 
My talk is called ``Boundary condition changing operators and singular vectors of Virasoro and
affine Lie algebra modules''. 
\end{document}

>>>>

Hello!
It's a great pleasure for me to be here in Simons Center for geometry and physics. 
My talk is called ``Boundary condition changing operators and singular vectors of Virasoro and
affine Lie algebra modules''.

Consider some simple two-dimensional lattice model, for example, Ising
model on hexagonal lattice. Let us study the behavior of domain walls.
In order to do it we need to look at the model on the bounded domain.
We take upper half-plane. Then impose boundary condition in such a way
that we have a domain wall from zero to infinity.

In critical model there is continuous limit. It is given by a solution
of Schramm-Loewner stochastic differential equation. 
\end{document}
